---
title: "GSS challange"
author: "Lelainy Saavedra"
date: "October 8,2020"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(knitr)
GSS <-read.csv(file="GSScsv.csv",header=TRUE)
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

Is belief in the bigbang theory (BIGBANG) independent of belief in an afterlife (POSTLIFE)? 

$H_O$: There is NO relationship between believing in the BigBang theory and believeing in Postlife. 

$H_A$:There Is a relationship between believing in the Bigbang theory and believing in Postlife.  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->
 The method I will be using will be a cat~cat templates because we have two categories.
 I will be using a barplot, and a chisquare because there are only 2 levels of categories. For more detail and a clear description of my results we have at the end a fisher' exact Test that will show us the P value and the ratios.
# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->



## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->  
###Plot barplots

```{r}
barchartGC(~BIGBANG + POSTLIFE, data=GSS)
barchartGC(~BIGBANG + POSTLIFE, data=GSS, type="percent")

```

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->  

```{r}
table1 <- xtabs(~BIGBANG + POSTLIFE, data=GSS)
rowPerc(table1)
colPerc(table1)
```
## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->  


```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```
In this Chisquare test, it shows that the P. value is of 0.0801, we can confirm these numbers by also looking at the Fisher's Exact Test for Count Data where it shows us that the true odds ratio is not equal to 1. This is not enough evidence that shows us that there IS a relationship between believing in The BigBang and believing in Postlife.



# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

We have concluded that because the charts do not show enough evidence to prove that there IS relationship between believing in the BiBang and believing in postlife, and the charts gave us a P value of 0.0801 we FAIL TO REJECT THE NULL HYPOTHESIS, we do not have enough evidence to reject it.  



  
